Co-citations in context

### 2019-09-15 Revision2Letter.tex
tweak

\vspace{5mm}
\raggedright 
Thank you for the opportunity to submit a revision. Again, we thank the reviewers for their diligence and professional courtesy. We have considered their comments and provide a response below. We have also responded to your suggestion that we include a discussion of the work of Wang, Veugelers, and Stephan. Our response is reflected in a revised manuscript with blue text indicating where changes have been made to the first revision or where we have made minor edits to assist clarity.

@@

Thus, the basis for arguing that reference counts generally correlates with citation counts seems a little shaky although it may be true for a narrow range and subset of articles (Figure 3, column 3 in particular). A number of factors help explain variance in citation counts (both Peters and van Raan \& Vieira and Gomes) and focusing on reference count alone is distracting to the purpose of our paper.

>>>>

\vspace{5mm}
\raggedright 
Thank you for the opportunity to submit a revision. Again, we thank the reviewers for their diligence and professional courtesy. We have considered their comments and provide a response below. We have also responded to your suggestion that we include a discussion of the work of Wang, Veugelers, and Stephan. Our response is also reflected in a revised manuscript with blue text indicating where changes have been made to the first revision or where we have made minor edits to assist clarity.

@@

Thus, the basis for arguing that reference counts generally correlates with citation counts seems a little shaky although it may be true for a narrow range and subset of articles (Figure 3, column 3 in particular). A number of factors help explain variance in citation counts (both Peters and van Raan \& Vieira and Gomes), particularly impact of publishing journal and impact of cited references so focusing on reference count alone seems distracting to the purpose of our paper.

### 2019-09-15 cocit_r_v3.tex
tweak

\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one. While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores. Such grouping, while appealing on account of its relative simplicity, obscures measurements of novel pairings at the article level. Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\citep{traag_louvain_2019, klavans_which_2017}}.  Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and appropriate consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.

>>>>

\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one. While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores. Such grouping, while appealing on account of its relative simplicity, obscures measurements of novel pairings at the article level. Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\citep{traag_louvain_2019, klavans_which_2017}.  We acknowledge the limitations of using citation counts to measure impact, a number of factors contribute to these counts\citep{peters_determinants_1994,vieira_citations_2010} and studying them further in the context of this study may be of interest, Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and appropriate consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}
